---
title: 'Data Visualization: Dashboard'
author: Molly Vonk
date: '2017-10-08'
slug: data-visualization-dashboard
categories:
  - R
tags:
  - Chart
  - Visualization
---

After installing the following packages:

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
library(flexdashboard)
```

In RStudio select New File, then R Markdown file. From the pop up screen select From Template and then Flex Dashboard. The markdown file is set up with a template in place for three graphs/charts. Use a new R Script file for your scratchwork in extracting and visualizing the data.

Example: Extract

```{r}
query<-"SELECT yearID,HR FROM Teams"

result<-sqldf(query)
```

Example: Visualize

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  xlab("Year")+
  ylab("Homeruns")
```

Then once your data is all set, simply compy and paste your work from the R Script file to the R Markdown file into their designated sections: Chart A, B, or C.

Be sure to change the Title names from Chart A, B, or C to the name for that specific chart or graph.


