---
title: 'Data Visualization: Scatter Plots'
author: Molly
date: '2017-09-27'
slug: data-visualization-scatter-plots
categories:
  - R
tags:
  - Visualization
  - Chart
---

After downloading and bringing in the following packages: Lahman, sqldf, and ggplot2. The first step is to extract the data from the Lahman database.

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

result<-sqldf(query)
```

Now the data has been saved under the results. The next step is to write out the commands for visualizing the data.

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR))
```

The Scatter Plot is incomplete still. Next step is to add proper titles to chart.

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR))+
  ggtitle("Career Strikeouts vs. Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homerunes")
```

It is also possible to change the size of the points and their color.

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR), size=3, color="blue")+
  ggtitle("Career Strikeouts vs. Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homerunes")
```