---
title: 'Data Visualization: Bar Plots'
author: Molly Vonk
date: '2017-10-08'
slug: data-visualization-bar-plots
categories:
  - R
tags:
  - Chart
  - Visualization
---

After downloading and bringing in the following packages: 

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Before collecting the data it is important to note the difference between a Factor and a Level. A Factor is the whole, while a Level is the part.

For example in a classroom of people one possible Factor could be hair color. Sarah's has blonde hair and Tyler has black hair. Sarah's Level would be blonde, while Tyler's Level would be black.

When using R it is important to be specific; to make sure that R understands what the Factors are and what the Levels are.

##### Example for writing the commands

Using Class Standing

```{r}
standing<-c("junior","freshman","junior","sophomore","senior")

standing<-factor(standing)
```

R organizes information alphabetically by default for the Levels. Therefore to set a specific order for the levels:

```{r}
standing<-c("junior","freshman","junior","sophomore","senior")

standing<-factor(standing,levels=c("freshman","sophomore","junior","senior"))
```

The first step for creating a Bar Plot chart is to extract the data from the Lahman database.

```{r}
query<-"SELECT name,HR
FROM Teams
WHERE yearID=1980
ORDER BY HR"

result<-sqldf(query)

result$name<-factor(result$name,levels=result$name)
```

The next step is to write the commands to visualize the data.

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()
```

Now you need to add the Titles.

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ylab("Homeruns")+
  xlab("Team")+
  ggtitle("1980 Team Homerun Distribution")
```

You can also change the colors on the chart.

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity',color='purple',fill='pink')+
  coord_flip()+
  ylab("Homeruns")+
  xlab("Team")+
  ggtitle("1980 Team Homerun Distribution")
```


