---
title: 'Data Visualization: Histograms'
author: Molly Vonk
date: '2017-10-02'
slug: data-visualization-histograms
categories:
  - R
tags:
  - Visualization
---

After downloading the following packages:

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

The first step is to extract the data from Lahman.
```{r}
query<-"SELECT weight
FROM Master"

result<-sqldf(query)
```

Now the data has been saved under results. The next step is to write the commands for visualizing the data.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight))
```

The Histogram could use a couple of edits to make the graph more legible. Such as changing the color to see the bars outline and changing the number of bars.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="green",bins=50)
```

Remember to add a proper title for the graph.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="green",bins=50)+
  ggtitle("Body-Weight Distribution for Baseball Players")
```

