---
title: 'Using RStudio: Filtering Columns and Rows'
author: Molly Vonk
date: '2017-11-18'
slug: using-rstudio-filtering-columns-and-rows
categories:
  - R
tags:
  - Chart
  - Visualization
---

## Filtering Columns and Rows

With SQL, you can filter columns and rows by using SELECT and WHERE. Let's look at an example using the Lahman database. So we should first load that database, along with the package sqldf.

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
```

Suppose now you would like to see the home run totals for the 1927 Yankees. You could write the following query:

```{r}
query<-"SELECT playerID,yearID,teamID,HR 
FROM Batting 
WHERE teamID='NYA' and yearID=1927"

sqldf(query)
```

Here are a few examples of filtering columns and rows using the Lahman database. Remember you still need to first load the Lahman database, along with the package sqldf if you have restarted a new session on RStudio.

##### Example 1:

Find all instances where Yankees have hit 40 home runs or more.

```{r}
query<-"SELECT playerID,yearID,teamID,HR
FROM Batting
WHERE teamID='NYA' and HR>=40"

sqldf(query)
```

As you can see in the above chart, the answer is 30 instances.

##### Example 2:

Find all instances where a player had more than 40 Home runs but less than 60 Strikeouts.

```{r}
query<-"SELECT playerID,yearID,teamID,HR,SO 
FROM Batting 
WHERE HR>40 and SO<60"

sqldf(query)
```

As you can see in the above chart, the answer is 28 instances.

It is important to note the changes in the query. SO was added to the SELECT list since you were looking for Strikeout data. Also since the example was for all teams, it was necessary to remove the teamID='NYA'. Also before running the new query, you must highlight the new query to specify that you want this new query run instead of the previous one.

##### Example 3:

Find all instances of Phillies in the 1970s hitting more than 30 Home runs.

```{r}
query<-"SELECT playerID,yearID,teamID,HR
FROM Batting
WHERE teamID='PHI' and HR>30 and yearID<=1979 and yearID>=1970"

sqldf(query)
```

As you can see in the above chart, the answer is 9 instances.

It is important to note the changes in the query. The team was now the Phillies, so this required teamID='PHI' instead of teamID='NYA'. Also because you were searching for instances throughout the 1970s, it was necessary to state that you were searching between 1970 and 1979. If only 1970 is written then every date from 1970 on will appear. Hence why it was important to have yearID<=1979.