---
title: 'Data Visualization: Time Series'
author: Molly Vonk
date: '2017-10-02'
slug: data-visualization-time-series
categories:
  - R
tags:
  - Chart
  - Visualization
---

After downloading and bringing in the following packages: 

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

The first step is to extract the data from the Lahman database.

```{r}
query<-"SELECT yearID,HR
FROM Batting
WHERE playerID='ruthba01'"

result<-sqldf(query)
```

The next step now that the data is saved under results is to type the commands to visualize the data.

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))
```

You can add lines to connect the points.

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))
```

Next step is to add the Titles.

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Ruth's Homerun Totals Throughout the Years")+
  xlab("year")+
  ylab("homeruns")
```

If you don't want the points to be on the graph , you can remove them by 'pounding them out'. This means that you simply place a # sign in front of the command line for the points.

```{r}
ggplot()+
  #geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Ruth's Homerun Totals Throughout the Years")+
  xlab("year")+
  ylab("homeruns")
```

